\documentclass{moderncv}

\usepackage[left=0.8in,top=0.8in,right=0.8in,bottom=0.8in]{geometry}
\moderncvtheme{classic}
\moderncvcolor{grey}  

\usepackage[utf8]{inputenc}
\usepackage{color}

% personal data
\firstname{\huge{Dario Alberto}  \vspace{3mm} \newline }
\familyname{Romero Fonseca}

\phone{(+1) 202 615 0988}
\email{dr2879@columbia.edu}
\address{420 West 118th Street}{New York, NY.}

\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}

% the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}
\definecolor{web}{rgb}{0.2,0.2,0.2}
%\definecolor{web}{rgb}{0.5,0.5,0.5}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\section{\textbf{Education}}
\cventry{2016--Today}{\textbf{Ph.D. Economics}}{Columbia University} {New York, USA}{}{}
\cventry{2011--2012}{\textbf{M.A. Economics}}{Universidad de los Andes} {Bogot\'a, Colombia}{}{}
\cventry{2007--2010}{\textbf{B.A. Political Science}}{Universidad de los Andes} {Bogot\'a, Colombia}{}{}
\cventry{2006--2010}{\textbf{B.A. Economics}}{Universidad de los Andes} {Bogot\'a, Colombia}{}{}

\section{\textbf{Research Fields of Interest}}
{Development Economics,  Political Economy,  Economic History and Empirical Methods }

\section{\textbf{Profesional Experience}}
\cventry{2014--2016}{\textbf{Inter-American Development Bank}}{Research Fellow} {}{}{Washington, DC USA. Person in Charge: Ph.D. Matias Busso.}
\cventry{2013--2014}{\textbf{J-PAL LAC}}{Research Analyst} {}{}{Santiago, Chile. Person in Charge: Ph.D. Francisco Gallego.}
\cventry{2010--2013}{\textbf{Universidad del Rosario}}{Research Assistant} {}{}{Bogot\'a, Colombia. Person in Charge: Ph.D. Juan Fernando Vargas.}

\section{\textbf{Publications}}
{Killing Social Leaders for Territorial Control: The Unintended Consequences of Peace, with Mounu Prem, Andres Rivera and Juan Vargas (forthcoming) \emph{Quarterly Journal of Political Science},\\}

{The Perils of High-Powered Incentives: Evidence from Colombia's False Positives, with Daron Acemoglu, Leopoldo Fergusson, James Robinson and Juan Fernando Vargas (2020). \emph{American Economic Journal}, vol. 12(3), pp.1- 43. \\ }  


{Improving Access to Preventive Maternal Health Care Using Reminders: Experimental Evidence from Guatemala. With Matias Busso and Dario Salcedo (2017), \emph{Economic Letters}, vol. 161, pp. 43-46.\\} 

{Books or laptops? The effect of shifting from printed to digital delivery of educational content on learning. With Rosangela Bando, Francisco Gallego and Paul J. Gertler (2017). \emph{Economics of Education Review}, vol. 61, pp. 162-173\\} 

{The effects of financial aid and returns information in selective and less selective schools: Experimental evidence from Chile. With Matias Busso, Taryn Dinkelman and Claudia Martínez (2017). \emph{Labour Economics}, Vol. 45, pp. 79-91.\\}

{Insecurity or Perception of Insecurity? Urban Crime and Dissatisfaction with Life: Evidence from the Case of Bogot\'a. (2014). \emph{Peace Economics, Peace Science and Public Policy}, Vol. 20(1), pp. 169-208.}

\section{\textbf{Chapters in Books}}
{Facts and Determinants of Female Labor Supply in Latin America, with Matias Busso. In “Bridging gender gaps? The rise and deceleration of female labor force participation in Latin America”, Leonardo Gasparini and Mariana Marchioni (Eds), 2015.}

\section{\textbf{Working Papers}}

{Labor Market Adjustment to Import Competition: Long-run Evidence from Establishment Data , with Juan Blyde and Matias Busso. IDB WORKING PAPER SERIES Nº IDB- WP -01100 \\}

{The Environmental Impact of Civil Conflict: The Deforestation Effect of Paramilitary Expansion in Colombia, with Leopoldo Fergusson and Juan F. Vargas, Cede Working Paper 2014-36.}

\section{\textbf{Work in progress}}
{Non-State Actors in Pandemic: Violence as a Territorial Control Strategy during COVID-19 (With Diego Martin) \\}

{Every Cloud has a Silver Lining: The Effect of Cotton Crisis on Spanish XIXth Century Textile Industry}\\

{The (unintended?) effects of US military training during the Cold War in Latin-America \\}

{Civilians in the Time of Counterinsurgency: The Consequences of Foreign Military Training in Colombia \\}

{Something Biased This Way Comes: The Effect of Media on Local Elections in US (With Haaris Maatin) }


\section{\textbf{Computer skills}}
\cvcomputer{Statistical}{Stata, SPSS, Eviews, R, Matlab}{Advanced}{Programming and Statistical Analysist}
\cvcomputer{Geographical}{ArcGIS, QGIS, GeoDa}{Advanced}{Quantitative and Statistical Analysist}
\cvcomputer{Word Processor}{MS Office, \LaTeX, Beamer} {Advanced}{Document Markup and Design}
\cvcomputer{Lenguages}{Phyton}{Basic}{Programming}


\section{\textbf{Languages}}
\cvlanguage{Spanish}{Native}{}
\cvlanguage{English}{Fluent}{}
\cvlanguage{Portuguese}{Advanced}{}
\cvlanguage{German}{Intermediate}{}
\cvlanguage{French}{Beginner}{}
\cvlanguage{Italian}{Beginner}{}



\end{document}